---
title: "noise model"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{R}
library(knitr)
summarizeVec <- function(dat){
  
  plot(dat, main="orignal signal")
  dat.fft = fft(dat)
  plot(dat.fft)
  
  print ("abs FFT")
  print(summary(abs(dat.fft)))
  print("Im")
  print(summary(Im(dat.fft)))
  print("Re")
  print(summary(Re(dat.fft)))
  
  print("highest abs")
  ordFFt=order(abs(dat.fft),decreasing = T)
  kable(as.data.frame(abs(dat.fft)[ordFFt[1:50]]))
  print("which highest abs")
  print(ordFFt[1:50])
  print ("highest 50 FFT values")
  print(abs(dat.fft)[ordFFt][1:50])
  hist(abs(dat.fft)[ordFFt][1:5000000])
  acf(dat, lag.max = 1000)
  
}

```


The goal of this markdown document is test if a faint signal can be detected under a lot of noise and how to do this.

We start off with the easiest scenario: a sinus function is hidden underneath some noise and we know the frequency:

# Sinus length 100

```{r first1, cache = TRUE}
summarizeVec(dat = sin(c(1:100)/10))

```


# Sinus length 1000

```{r first2, cache = TRUE}
summarizeVec(dat = sin(c(1:1000)/10))

```

# Sinus length 10,000,000

```{r first3, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
}else{
  summarizeVec(dat = sin(c(1:10000000)/10))
}


```


# Sinus length 10,000 + noise min = -1000, max = 1000


```{r first4, cache = TRUE}
dat = sin(c(1:10000)/10)
summarizeVec(dat = dat + runif(length(dat), min = -1000, max = 1000))

```



```{r }
n=1000
for(idx in c(1:n)){
  dat = dat + sin(c(1:1000)/10)
  dat = dat + runif(length(dat), min = -1000, max=1000)
}
plot(dat, main=paste("org data +noise * ",n))
acf(dat, lag.max = 1000)
Sys.time()
```

```{r rand10K, cache = TRUE}
n=10000
dat = sin(c(1:1000)/10)
for(idx in c(1:n)){
  dat = dat + sin(c(1:1000)/10)
  dat = dat + runif(length(dat), min = -1000, max=1000)
}
plot(dat, main=paste("org data +noise * ",n))
acf(dat, lag.max = 1000)
Sys.time()
```

The function *acf* computes (and by default plots) estimates of the autocovariance or autocorrelation function. Function pacf is the function used for the partial autocorrelations. Function ccf computes the cross-correlation or cross-covariance of two univariate series.



```{r rand100K, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
}else{
  n=100000
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin(c(1:1000)/10)
    dat = dat + runif(length(dat), min = -1000, max=1000)
  }
  plot(dat, main=paste("org data +noise * ",n))
  acf(dat, lag.max = 1000)
  Sys.time()
}
```

```{r rand 1M, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
}else{
  n=1000000
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin(c(1:1000)/10)
    dat = dat + runif(length(dat), min = -1000, max=1000)
  }
  plot(dat, main=paste("org data +noise * ",n))
  acf(dat, lag.max = 1000)
  Sys.time()
}
```

```{r rand 10M, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
}else{
  n=10000000
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin(c(1:1000)/10)
    dat = dat + runif(length(dat), min = -1000, max=1000)
  }
  plot(dat, main=paste("org data +noise * ",n))
  acf(dat, lag.max = 1000)
  Sys.time()
}
```


```{r rand 10M0-1000, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
}else{
  n=10000000
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin(c(1:1000)/10)
    dat = dat + runif(length(dat), min =0, max=1000)
  }
  plot(dat, main=paste("org data +noise * ",n))
  acf(dat, lag.max = 1000)
  Sys.time()
}
```


We know that our signal is between -1 and 1 and the noise is between -1000 and 1000, thus a factor 1000 difference. We see that with 1000 * 1000 we see the signal. Is it by  chance that it is square of the ratio?

Let's redo with 100 instead of 1000

```{r first-b, cache = TRUE}
dat = sin(c(1:1000)/10)
plot(dat, main="orignal signal")
dat = dat + runif(length(dat), min = -100, max=100)
plot(dat, main="org data +noise")

n=1000
for(idx in c(1:n)){
  dat = dat + sin(c(1:1000)/10)
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, main=paste("org data +noise * ",n))
acf(dat, lag.max = 1000)
Sys.time()
```

```{r rand10K-b, cache = TRUE}
n=10000
dat = sin(c(1:1000)/10)
for(idx in c(1:n)){
  dat = dat + sin(c(1:1000)/10)
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, main=paste("org data +noise * ",n))
acf(dat, lag.max = 1000)
Sys.time()
```

```{r rand100K-b, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin(c(1:1000)/10)
    dat = dat + runif(length(dat), min = -100, max=100)
  }
  plot(dat, main=paste("org data +noise * ",n))
  acf(dat, lag.max = 1000)
  Sys.time()

```

```{r rand 1M-b, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin(c(1:1000)/10)
    dat = dat + runif(length(dat), min = -100, max=100)
  }
  plot(dat, main=paste("org data +noise * ",n))
  acf(dat, lag.max = 1000)
  Sys.time()

```

```{r rand 10M-b, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin(c(1:1000)/10)
    dat = dat + runif(length(dat), min = -100, max=100)
  }
  plot(dat, main=paste("org data +noise * ",n))
  acf(dat, lag.max = 1000)
  Sys.time()

```


This gives us already an idea that we need x^2 samples where x is the ratio between signal and noise.

## how large can the noise be? 

Given that we measure at 12 bit (this what is usally done, but i need confirmation from Galle & Co.) we can get values between 0 and 2^12-1 = 4095.
Thus in the worst case we need (2^12)^2 samples ~=17 Million samples. This is in the case that the max noise level reaches 4000 and our signal is at one. I guess the signal should be around 10 and the noise around 1000 max, thus we need about 10,000 samples.

From what I remember from my mom, she can get a measurement in less than a second. So if we need 1 second per measurement we would need to aquire 17M / 60 (seconds) / 60 (minutes) / 24 (hours) ~= 200 days of measurements...

For the more reasonable case of 10,000 samples we would need 10,000 / 60/60 ~= 3 hrs of capture.

There is still one small catch...
we would need a continous capture and I am not sure that the redpitaya can do this...

But there are packages in R that can deal with this type of problem...

Why do we need a continous capture? 
Because without knowing the exact time context we cannot correctly align the spectra. So let's see what happens if we add some noise to the x-axis:

here we add noise to x: runif gives values between -1 and + 1 we add this to the x values which go from 1 to 1000. We devide by 10 to capture more details of the sinus function.
n is the number of repetions we do. This is a bit slower than multiplying but less dangerous in terms of introducing errors since I believe i understand this way better...

```{r rand 1M-b-normal 0.001, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
  noiseXFactor=0.001
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin((c(1:1000)+ runif(1000)*noiseXFactor)/10 )
    dat = dat + runif(length(dat), min = -100, max=100)
  }
  plot(dat, main=paste("org data +noise * ",n, " nF:", noiseXFactor))
  acf(dat, lag.max = 1000)
  Sys.time()

```


```{r rand 1M-b-normal 0.01, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
  noiseXFactor=0.01
  dat = sin(c(1:1000)/10)
  for(idx in c(1:n)){
    dat = dat + sin((c(1:1000)+ runif(1000)*noiseXFactor)/10 )
    dat = dat + runif(length(dat), min = -100, max=100)
  }
  plot(dat, main=paste("org data +noise * ",n, " nF:", noiseXFactor))
  acf(dat, lag.max = 1000)
  Sys.time()

```





```{r rand 1M-b-normal 0.1, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
  dat = sin(c(1:1000)/10)
  noiseXFactor=0.1
  for(idx in c(1:n)){
    dat = dat + sin((c(1:1000)+ runif(1000)*noiseXFactor)/10 )
    dat = dat + runif(length(dat), min = -100, max=100)
  }
  plot(dat, main=paste("org data +noise * ",n, " nF:", noiseXFactor))
  acf(dat, lag.max = 1000)
  Sys.time()

```


```{r rand 1M-b-normal 0.2, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
  dat = sin(c(1:1000)/10)
  noiseXFactor=0.2
  for(idx in c(1:n)){
    dat = dat + sin((c(1:1000)+ runif(1000)*noiseXFactor)/10 )
    dat = dat + runif(length(dat), min = -100, max=100)
  }
  plot(dat, main=paste("org data +noise * ",n, " nF:", noiseXFactor))
  acf(dat, lag.max = 1000)
  Sys.time()

```


```{r rand 1M-b-normal pi, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=pi
for(idx in c(1:n)){
  dat = dat + sin((c(1:1000)+ runif(1000)*noiseXFactor)/10 )
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, main=paste("org data +noise * ",n, " nF:", noiseXFactor))
acf(dat, lag.max = 1000)
Sys.time()

```


```{r rand 1M-b-normal 1, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=1
for(idx in c(1:n)){
  dat = dat + sin((c(1:1000)+ runif(1000)*noiseXFactor)/10 )
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, main=paste("org data +noise * ",n, " nF:", noiseXFactor))
acf(dat, lag.max = 1000)
Sys.time()

```


```{r rand 1M-b-normal 10, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=10
for(idx in c(1:n)){
  dat = dat + sin((c(1:1000)+ runif(1000)*noiseXFactor)/10 )
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, main=paste("org data +noise * ",n, " nF:", noiseXFactor))
acf(dat, lag.max = 1000)
Sys.time()

```

We see that the noise on the x-axis is somehow not relevant... (only if it is multiplyer of pi...)

Next, let's simulate what happens if we add sections that are not aligned, like we take multiple measurements of lenght X and just add them on top of each other... That is we shift the sinus by a random number for each iteration

```{r multimeasure, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=3
for(idx in c(1:n)){
  dat = dat + sin((c(1:1000)+ runif(1)*noiseXFactor)/10 )
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift"))
acf(dat, lag.max = 1000)
Sys.time()

```


what happens if we have multiple sinus that have different amplitudes and  frequencies

# Two:

amp=c(1,5)
frq=1/c(1,5)

```{r multi signal, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=3
amp=c(1,5)
frq=1/c(1,5)
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000)+ runif(1)*noiseXFactor)/frq[nsi] )
  }
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift, \nmulti signal: frq: ", paste(frq, collapse = ", "), "amp:", paste(amp,collapse = ", ")))
acf(dat, lag.max = 1000)
Sys.time()

```
amp=c(1,5)
frq=1/c(1,1)

```{r multisignal 2, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=3
amp=c(1,5)
frq=1/c(1,1)
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000)+ runif(1)*noiseXFactor)/frq[nsi] )
  }
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift, \nmulti signal: frq: ", paste(frq, collapse = ", "), "amp:", paste(amp,collapse = ", ")))
acf(dat, lag.max = 1000)
Sys.time()

```
amp=c(1,100)
frq=1/c(1,100)

```{r multisignal 3, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=3
amp=c(1,100)
frq=1/c(1,100)
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000)+ runif(1)*noiseXFactor)/frq[nsi] )
  }
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift, \nmulti signal: frq: ", paste(frq, collapse = ", "), "amp:", paste(amp,collapse = ", ")))
acf(dat, lag.max = 1000)
Sys.time()

```
amp=c(1,100)
frq=1/c(1,2)

```{r multisignal 4, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=3
amp=c(1,100)
frq=1/c(1,2)
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000)+ runif(1)*noiseXFactor)/frq[nsi] )
  }
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift, \nmulti signal: frq: ", paste(frq, collapse = ", "), "amp:", paste(amp,collapse = ", ")))
acf(dat, lag.max = 1000)
Sys.time()

```
amp=c(1,100)
frq=1/c(1,1.1)

```{r multisignal 5, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=3
amp=c(1,100)
frq=1/c(1,1.1)
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000)+ runif(1)*noiseXFactor)/frq[nsi] )
  }
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift, \nmulti signal: frq: ", paste(frq, collapse = ", "), "amp:", paste(amp,collapse = ", ")))
acf(dat, lag.max = 1000)
Sys.time()

```

# multiple
amp=sample(1:100, 20)
frq=1/sample(1:100, 20)

```{r multisignal 6, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=3
amp=sample(1:100, 20)
frq=1/sample(1:100, 20)
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000)+ runif(1)*noiseXFactor)/frq[nsi] )
  }
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift, \nmulti signal: frq: ", paste(frq, collapse = ", "), "\namp:", paste(amp,collapse = ", ")))
acf(dat, lag.max = 1000)
Sys.time()

```

amp=sample(1:1000, 200)
frq=1/sample(1:1000, 200)


```{r multisignal 7, cache = TRUE}
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
dat = sin(c(1:1000)/10)
noiseXFactor=3
amp=sample(1:1000, 200)
frq=1/sample(1:1000, 200)
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000)+ runif(1)*noiseXFactor)/frq[nsi] )
  }
  dat = dat + runif(length(dat), min = -100, max=100)
}
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift, \nmulti signal: frq: ", paste(frq, collapse = ", "), "\namp:", paste(amp,collapse = ", ")))
acf(dat, lag.max = 1000)
Sys.time()

```

## identify frequencies and amplitudes, decompose


now what happens if everything has one or more frequency? We would have millions of signals at the same time. The noise would actually be the signal.
We would have to figure out the one signal that distinguishes between the sample and the control. We have a classification problem.

Or we can do this simply by aligning and substracting two different spectra?

Before investigating classification methods let's look at if and how we can decopose a given spectrum.

```{r decompose, cache = TRUE }
plot(dat, type='l',main=paste("org data +noise * ",n, " nF:", noiseXFactor, "shift, \nmulti signal: frq: ", paste(frq, collapse = ", "), "\namp:", paste(amp,collapse = ", ")))
acf(dat, lag.max = 1000)

fit = stl(ts(dat,frequency = 100), s.window = 21)
plot(fit)

decompose(ts(dat,frequency = 100), type = c("additive"))

```

```{r}
library("Rlibeemd")
library(dplyr)
ceedat = ceemdan(ts(dat,frequency = 100), ensemble_size = 1000)
plot(ceedat, main = " IMFs and residual extracted by CEEMDAN algorithm")
```

Binary vector genetic algorithm. This has the advantage of having much fewer possibilities as we can only generate 2^7 = 128 different values per parameter, and the crossover has potentially greate effects. We run the GA multiple times and carry over the best. I.e. something like a GA of an GA that allows for finding better local minima.

we need to check if the neighbors, i.e. the mutations with only one substitution have similar values.

```{r genalg, eval=FALSE}
nSin = 2 # number of sinus curves to add
if (Sys.info()["nodename"] == "berndCIH.local") {
  print("development version")
  n=100
}else{
  n=1000000
}
# init 
amp=sample(1:100, nSin)
frq=sample(1:100, nSin)
#generate data
dat = rep(0,1000) 
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000))*frq[nsi] )
  }
  #dat = dat + runif(length(dat), min = -100, max=100)
}
# plot added sinus curve
par(mfrow=c(1,1))
plot(dat, type='l')    
#Which signal to be found
x=c(amp,frq)
genBinDat <- function(x) {
  nBin=7
  xstr=paste0(as.character(x),collapse = "")
  x=xstr %>% substring(seq(1,nchar(xstr)-1,nBin),
                       seq(nBin,nchar(xstr)+1,nBin)) %>% strtoi(base=2)
  len = length(x)
  len2 = len/2
  lenVec = length(dat)
  amp=x[1:len2]
  frq=x[(len2+1):len]
  datEv=rep(0,lenVec)
  for (nsi in 1:length(frq)){
    datEv = datEv + amp[nsi] * sin(c(1:lenVec)*frq[nsi] )
  }
  #plot(datEv, type='l')
  datEv = datEv - min(datEv)
  datEv = datEv/max(datEv)
  #plot(datEv, type='l')
  
  return(datEv)
}
plot(genBinDat(x), type='l',main="orginal")

n2bin <- function(x){
  
}

ampOrg = amp
freqOrg = frq
xOrg=c(ampOrg,freqOrg)


library(genalg)
library(ggplot2)
#The genalg algorithm tries to optimize towards the minimum value. 
datOrg = dat

max(dat)
min(dat)
dat = dat - min(dat)
dat = dat/max(dat)

evalFunc <- function(x) {
  len = length(x)
  len2 = length(x)/2
  lenVec = length(dat)
  amp=x[1:(length(x)/2)]
  frq=x[(len2+1):(len)]
  datEv=rep(0,lenVec)
  for (nsi in 1:length(frq)){
    datEv = datEv + amp[nsi] * sin((c(1:lenVec))*frq[nsi] )
  }
  
  datEv = datEv - min(datEv)
  datEv = datEv/max(datEv)
  # return(sum(sqrt((dat - datEv)^2)))
  return(as.numeric(dist(matrix(c(dat,datEv),nrow = 2,byrow=T))))
}
evalFunc(x)


library(dplyr)
#x=c(0,1,0,1,0,0,0,0,1,0,0,1,0,0,0,0,1,0,1,0,1,0,1,0,0,0,0,0)
#strtoi(paste0(as.character(x),collapse = ""),base=2)
evalBinFunc <- function(x) {
  nBin=7
  xstr=paste0(as.character(x),collapse = "")
  x=xstr %>% substring(seq(1,nchar(xstr)-1,nBin),
                       seq(nBin,nchar(xstr)+1,nBin)) %>% strtoi(base=2)
  len = length(x)
  len2 = length(x)/2
  lenVec = length(dat)
  amp=x[1:(length(x)/2)]
  frq=x[(len2+1):(len)]
  datEv=rep(0,lenVec)
  for (nsi in 1:length(frq)){
    datEv = datEv + amp[nsi] * sin((c(1:lenVec))*frq[nsi] )
  }
  
  datEv = datEv - min(datEv)
  datEv = datEv/max(datEv)
  if(is.na(datEv) %>% sum >0) return (999999999999)
  # return(sum(sqrt((dat - datEv)^2)))
  return(as.numeric(dist(matrix(c(dat,datEv),nrow = 2,byrow=T))))
}

evalBinFunc(x)


st=1
monitor <- function(obj) {
  # plot the population
  xlim = c(obj$stringMin[1], obj$stringMax[1]);
  ylim = c(obj$stringMin[2], obj$stringMax[2]);
  #    plot(obj$population, xlim=xlim, ylim=ylim,xlab="x[1]", ylab="x[2]", cex = .1, main=paste(st,":",Sys.time()));
  bestVec[(iter*(idx-1)+1):(iter*idx)] <<- obj$best
  plot(log(bestVec[!is.na(bestVec)]), cex = .1, type='l', main=paste(st,":",Sys.time(), ":", idx));
  st<<-st+1
}

GAmodel=list()
nrepeat=100000
iter = 10
bestVec=rep(NA,nrepeat*iter)

#suggestions = matrix(c(1,1,1,1),nrow = 1)
suggestions = matrix(rep(1,28),nrow = 1)
dim(suggestions)
for (idx in 1:nrepeat){
  st=1
  #  GAmodel[[idx]] <- rbga(stringMin = rep(0,2*nSin), 
  #                         stringMax = c(rep(100,nSin),rep(100,nSin)),  
  GAmodel[[idx]] <- rbga.bin(size=28,  
                             popSize = 2800, iters = iter, 
                             mutationChance = 0.1, elitism = T, 
                             #evalFunc = evalFunc,  
                             evalFunc = evalBinFunc,  
                             monitorFunc=monitor, 
                             suggestions = suggestions,
                             verbose=T)
  currRet = apply(GAmodel[[idx]]$population, 1, evalBinFunc)
  suggestions = matrix(GAmodel[[idx]]$population[
    which(min(currRet)==currRet)[1]
    ,],nrow = 1)
}

cat(summary(GAmodel))

y=GAmodel[[idx-1]]$population[1,]
evalBinFunc(y)

plot(genDat(xOrg), type='l')
plot(genDat(y), type='l')
plot(genDat(y)-genDat(xOrg), type='l')
evalFunc(xOrg)
evalFunc(y)
y
xOrg


plot.new()
par(mfrow=c(2,5))

for(idx in 1:15){
  y=GAmodel[[idx]]$population[1,]
  plot(genDat(y)-genDat(xOrg), type='l', main=idx)
}


# best return values
GAmodel$best
# current population
GAmodel$population

currRet = apply(GAmodel$population, 1, evalFunc)
GAmodel$population[which(min(currRet)==currRet),]



monitor(GAmodel)

```

reelle genetic algorithm


```{r genalgRell}
nSin = 2 # number of sinus curves to add
n=100000 # number of samples to add
# init 
amp=sample(1:100, nSin)
frq=sample(1:100, nSin)
#generate data
dat = rep(0,1000) 
for(idx in c(1:n)){
  for (nsi in 1:length(frq)){
    dat = dat + amp[nsi] * sin((c(1:1000))*frq[nsi] )
  }
  #dat = dat + runif(length(dat), min = -100, max=100)
}
# plot added sinus curve
par(mfrow=c(1,1))
plot(dat, type='l')    
#Which signal to be found
x=c(amp,frq)
genDat <- function(x) {
  len = length(x)
  len2 = len/2
  lenVec = length(dat)
  amp=x[1:len2]
  frq=x[(len2+1):len]
  datEv=rep(0,lenVec)
  for (nsi in 1:length(frq)){
    datEv = datEv + amp[nsi] * sin(c(1:lenVec)*frq[nsi] )
  }
  #plot(datEv, type='l')
  datEv = datEv - min(datEv)
  datEv = datEv/max(datEv)
  #plot(datEv, type='l')
  
  return(datEv)
}
plot(genDat(x), type='l',main="orginal")

```

```{r}

ampOrg <- amp
freqOrg <- frq
xOrg <- c(ampOrg, freqOrg)


library(genalg)
library(ggplot2)
# The genalg algorithm tries to optimize towards the minimum value.
datOrg <- dat

max(dat)
min(dat)
dat <- dat - min(dat)
dat <- dat / max(dat)

evalFunc <- function(x) {
  len <- length(x)
  len2 <- length(x) / 2
  lenVec <- length(dat)
  amp <- x[1:(length(x) / 2)]
  frq <- x[(len2 + 1):(len)]
  datEv <- rep(0, lenVec)
  for (nsi in 1:length(frq)) {
    datEv <- datEv + amp[nsi] * sin((c(1:lenVec)) * frq[nsi])
  }

  datEv <- datEv - min(datEv)
  datEv <- datEv / max(datEv)
  # return(sum(sqrt((dat - datEv)^2)))
  return(as.numeric(dist(matrix(c(dat, datEv), nrow = 2, byrow = T))))
}
evalFunc(x)



st <- 1
monitor <- function(obj) {
  # plot the population
  xlim <- c(obj$stringMin[1], obj$stringMax[1])
  ylim <- c(obj$stringMin[2], obj$stringMax[2])
  #    plot(obj$population, xlim=xlim, ylim=ylim,xlab="x[1]", ylab="x[2]", cex = .1, main=paste(st,":",Sys.time()));
  bestVec[(iter * (idx - 1) + 1):(iter * idx)] <<- obj$best
  plot(log(bestVec[!is.na(bestVec)]), cex = .1, type = "l", main = paste(st, ":", Sys.time(), ":", idx))
  st <<- st + 1
}

GAmodel <- list()
if (Sys.info()["nodename"] == "berndCIH.local") {
  nrepeat <- 10
} else {
  nrepeat <- 100000
}
iter <- 10
bestVec <- rep(NA, nrepeat * iter)

suggestions <- matrix(c(1, 1, 1, 1), nrow = 1)
dim(suggestions)
for (idx in 1:nrepeat) {
  st <- 1
  GAmodel[[idx]] <- rbga(
    stringMin = rep(0, 2 * nSin),
    stringMax = c(rep(100, nSin), rep(100, nSin)),
    popSize = 2800, iters = iter,
    mutationChance = 0.1, elitism = T,
    evalFunc = evalFunc,
    monitorFunc = monitor,
    suggestions = suggestions,
    verbose = T
  )
  currRet <- apply(GAmodel[[idx]]$population, 1, evalFunc)
  suggestions <- matrix(GAmodel[[idx]]$population[
    which(min(currRet) == currRet)[1],
  ], nrow = 1)
}

cat(summary(GAmodel))

y <- GAmodel[[idx - 1]]$population[1, ]
evalBinFunc(y)

plot(genDat(xOrg), type = "l")
plot(genDat(y), type = "l")
plot(genDat(y) - genDat(xOrg), type = "l")
evalFunc(xOrg)
evalFunc(y)
y
xOrg


plot.new()
par(mfrow = c(2, 5))

for (idx in 1:15) {
  y <- GAmodel[[idx]]$population[1, ]
  plot(genDat(y) - genDat(xOrg), type = "l", main = idx)
}


# best return values
GAmodel$best
# current population
GAmodel$population

currRet <- apply(GAmodel$population, 1, evalFunc)
GAmodel$population[which(min(currRet) == currRet), ]



monitor(GAmodel)
```

